---
title: "Lab 1"
author: "Jason Flower"
date: "January 18, 2018"
output: html_document
self_contained: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Step 1 Load tidyverse


```{r load_packages}
library(tidyverse)
```

#Step 2 Get the data

```{r get_data}
hp_aggression <- read_csv("hp_aggression.csv")
```


#Step 3. Data wrangling

-select(): select specified columns from a df
-filter(): select rows by setting conditions to match
-mutate(): adds columns based on caclultions for existing
-arrange(: sorting variables
-group_by(): assign groupings to variable entries and can perform operations by group

```{r data_wrangling}
hp_df1 <- hp_aggression %>% 
  select(Name, aggressions, mentions) %>% 
  mutate(rate = aggressions/mentions) %>%
  group_by(Name) %>%
  mutate(average_rate = mean(rate)) %>%
  ungroup() %>%
  select(Name, average_rate) %>%
  distinct(Name, average_rate) %>%
  arrange(-average_rate) %>% #low to high rather than high to low
  head(10)

#alternative code
hp_df2 <- hp_aggression %>% 
  select(Name, aggressions, mentions) %>% 
  group_by(Name) %>%
  summarise(average_rate = mean(aggressions/mentions)) %>%
  ungroup() %>%
  arrange(-average_rate) %>% #low to high rather than high to low
  head(10)

```

##Step 4 ggplot refresher

1. Tell R that you want to use ggplot
2. Tell it what data you want to use (including what x and y are)
3. Tell it what type of graphic you want to create

```{r st_levels}

hp_df1$Name <- factor(hp_df1$Name, levels = hp_df1$Name[order(hp_df1$average_rate)])
```

Make the graph!

```{r hp_graph}
ggplot(data = hp_df1, aes(x = Name, y = average_rate)) +
  geom_bar(stat = "identity", aes(fill = Name)) +
  coord_flip()
```

